Chess collusion with hyper3 objects

### 2025-12-28 inst/collusion3.Rmd
need the magrittr package explicitly now
whitespace

```{r,label=loadjavelinandconvert}
cur_matches <- read.table("stockholm1962_matches.txt",header=FALSE)
colnames(cur_matches) <- c("white","black","result")
head(cur_matches)
nrow(cur_matches)
```

@@

```{r,try11and1888,cache=TRUE}
H3 <- f(1.1,1.888)
```

@@

```{r,testH3,cache=TRUE}
equalp.test(H3,n=1)
```

```{r,comparelikelihoods,cache=TRUE}
m1121 <- maxp(f(1.1,2.1),n=1,give=TRUE)
m1123 <- maxp(f(1.1,2.3),n=1,give=TRUE)
```

```{r,showmaxpwithlam}
pie(m1121$par)
```

@@

```{r,label=defineprofilelike,cache=FALSE}
profl <- function(v){
    lambda <- v[1]
    D <- v[2]
    H <- f(lambda,v)
    return(loglik(maxp(H,n=1),H))
}
```

@@

```{r,calcproflike,cache=TRUE}
profl(c(1.1,2.1))
#profl(c(1.2,2.1))
```

```{r,calcmanyproflike,cache=TRUE} 
np <- 4
lambda <- seq(from=0.1,to=1.5,len=np)
D <- seq(from=0.1,to=0.4,len=np)
jj <- as.matrix(expand.grid(lambda,D))
LL <- apply(jj,1,profl)
LL
```

>>>>

```{r, label=loadandconvert}
cur_matches <- read.table("stockholm1962_matches.txt", header=FALSE)
colnames(cur_matches) <- c("white", "black", "result")
head(cur_matches)
nrow(cur_matches)
```

@@

```{r, try11and1888, cache=TRUE}
H3 <- f(1.1, 1.888)
```

@@

```{r, testH3, cache=TRUE}
equalp.test(H3,n=1)
```

```{r, comparelikelihoods, cache=TRUE}
m1121 <- maxp(f(1.1,2.1), n=1, give=TRUE)
m1123 <- maxp(f(1.1,2.3), n=1, give=TRUE)
```

```{r, showmaxpwithlam}
pie(m1121$par)
```

@@

```{r, label=defineprofilelike, cache=FALSE}
profl <- function(v){
    lambda <- v[1]
    D <- v[2]
    H <- f(lambda,v)
    return(loglik(maxp(H,n=1),H))
}
```

@@

```{r, calcproflike, cache=TRUE}
profl(c(1.1,2.1))
```

```{r, calcmanyproflike, cache=TRUE} 
np <- 4
lambda <- seq(from=0.1, to=1.5, len=np)
D <- seq(from=0.1, to=0.4, len=np)
jj <- as.matrix(expand.grid(lambda, D))
LL <- apply(jj, 1, profl)
LL
```
